---
title: "Final Presentation"
author: "Author: Cindy Candelario Jose"
date: "`r format(Sys.time(), '%B %d, %Y @ %I:%M %p')`"
output: ioslides_presentation
---

```{r global options, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  comment = NA
)
```


## Packages Used

I used the tidyverse package to use the geom_bar and geom_boxplot functions to graph the data.

```{r, echo = TRUE}
library(tidyverse)
```

## Right to Work Membership Dataset

The dataset used in the presentation is from the website, Kaggle (https://www.kaggle.com/datasets/brandonconrady/right-to-work-dataset). This dataset focuses on union information for each state. 

**Variables in the Dataset:**

* `StateName`: Name of State
* `StateAbbrev`: State Name Abbreviation
* `Region`: US Geographical Region
* `RightToWork`: Right to work status
* `Year`: Year for data

##

* `UnionMembership`: Percentage of union members in the workforce
* `UnionRepresentation`: Percentage of workforce represented by unions
* `Difference`: Difference between union representation and union membership

```{r}
union_data <- read_csv("RTW_Membership.csv")

glimpse(union_data)
```

## Right to Work Membership Barplot

```{r, fig.align = "center", fig.width = 7.5}
ggplot(union_data, aes(x = UnionMembership, y = Region, fill = Region)) +
  geom_bar(stat = "identity") +
  scale_fill_brewer(palette = "YlGnBu") +
  labs(title = "Percentage of Union Membership in US regions",
       caption = "*data shown is taken from 2020-2021",
       x = "Percentage of Workforce Union Members",
       y = "Region in the US") 
```



## Right To Work Dataset

The data in Right to Work dataset is from the website, Kaggle (https://www.kaggle.com/datasets/brandonconrady/right-to-work-dataset?select=RightToWork.csv). 

**Variables in the Dataset:**

* `StateName`: Name of State
* `StateAbbrev`: State Name Abbreviation
* `Region`: US Geographical Region
* `RightToWork`: Right to work status

##

* `UnionMemberDensity2021`: Percent of union members in 2021
* `PovertyRate2022`: Poverty rate for each state in 2022
* `MedianHouseholdIncome2022`: Median household income in 2022

```{r}
job_data <- read_csv("RightToWork.csv")

glimpse(job_data)
```
## Right to Work Boxplot

```{r, fig.align = "center", fig.width = 7.5}
ggplot(job_data, aes(x = Region, y = UnionMemberDensity2021, fill = Region)) +
  geom_boxplot() +
  scale_fill_brewer(palette = "RdPu") +
  labs(title = "Percentage of Union Membership in 2021 in different US Regions", 
       x = "Region",
       y = "Union Membership")
  
```
